Data Management Plan

### 2021-11-30 application/dataManagementPlan_long.tex
Ammended Sec 5 and fixed typos

\section{Data sharing and access}
\subsection{Where will data be shared?}
% Identify any data repository (-ies) that are, or will be, entrusted with storing, curating and/or sharing data from your study, where they exist for particular disciplinary domains or data types.
Software modules will be available on Github and on Zenodo for long-term
preservation, with links from the Bonsai project site
(\url{https://bonsai-rx.org}) and available through the Bonsai system's package
management interface. Tutorials on how to use the added machine learning
functionality will be available at the Bonsai project site
(\url{https://bonsai-rx.org}) and automatically generated API documentation for
this functionality will be available through ReadTheDocs [\url{https://readthedocs.org/}].

@@

Several factors will contribute to the reusability of new functionality
incorporated into Bonsai. Code implementing this functionality will be
available in Github and Zenodo, under the permissive MIT license. Emphasis on standard and
uniform code style, achieved with the help of code review and paired
programming, will generate readable code, easier to read and extend by third
parties. Automated build methods will simplify code building and encourage
modification by new developers. Test cases with large coverage will motivate
software developers to modify Bonsai, without the risk of introducing
undetected bugs into the software. Carefully designed software, with simple and
clear object interfaces, will simplify the reuse of the proposed software.

@@

The project collaborator, NeuroGEARS Ltd, and its lead, Dr.~Gon\c{c}alo Lopes, have extended experience of software management and distribution, and will support our efforts.  In addition we will benefit from advice from UCL's recently established Centre for Advanced Research Computing.

>>>>

\section{Data sharing and access}
\subsection{Where will data be shared?}
% Identify any data repository (-ies) that are, or will be, entrusted with storing, curating and/or sharing data from your study, where they exist for particular disciplinary domains or data types.
Software modules will be available on GitHub and on Zenodo for long-term
preservation, with links from the Bonsai project site
(\url{https://bonsai-rx.org}) and available through the Bonsai system's package
management interface. Tutorials on how to use the added machine learning
functionality will be available at the Bonsai project site
(\url{https://bonsai-rx.org}) and automatically generated API documentation for
this functionality will be available through ReadTheDocs [\url{https://readthedocs.org/}].

@@

Several factors will contribute to the reusability of new functionality
incorporated into Bonsai. Code implementing this functionality will be
available in GitHub and Zenodo, under the permissive MIT license. Emphasis on standard and
uniform code style, achieved with the help of code review and paired
programming, will generate readable code, easier to read and extend by third
parties. Automated build methods will simplify code building and encourage
modification by new developers. Test cases with large coverage will motivate
software developers to modify Bonsai, without the risk of introducing
undetected bugs into the software. Carefully designed software, with simple and
clear object interfaces, will simplify the reuse of the proposed software.

@@

The project collaborator, NeuroGEARS Ltd, and its lead, Dr.~Gon\c{c}alo Lopes,
have extended experience of software management and distribution, and will
support our efforts. In addition we will benefit from advice from the UCL
Research Data Management group and from the recently established UCL's Centre
for Advanced Research Computing. Local storage platforms at the SWC/GCNU,
totaling more than six petabytes in storage space, will be used to mirror                                                                            
GitHub repositories.
